Computing Entropies With Nested Sampling

### 2017-03-16 paper/ms.tex
Working on the algorithm
More work on the algorithm
Fix in appendix

\usepackage{dsfont}
\usepackage[utf8]{inputenc}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{natbib}
\usepackage{enumerate}
\usepackage{microtype}

@@

This is difficult to compute because the expression
for the posterior distribution
\begin{align}
p(\x | \d) &= \frac{p(\x)p(\d | \x)}{p(\d)}
\end{align}
contains the marginal likelihood $p(\d)$.

@@

\begin{algorithm}
\caption{Calculate $y = x^n$}
\begin{algorithmic} 
\REQUIRE $n \geq 0 \vee x \neq 0$
\ENSURE $y = x^n$
\STATE $y \leftarrow 1$
\IF{$n < 0$}
\STATE $X \leftarrow 1 / x$
\STATE $N \leftarrow -n$
\ELSE
\STATE $X \leftarrow x$
\STATE $N \leftarrow n$
\ENDIF
\WHILE{$N \neq 0$}
\IF{$N$ is even}
\STATE $X \leftarrow X \times X$
\STATE $N \leftarrow N / 2$
\ELSE[$N$ is odd]
\STATE $y \leftarrow y \times X$
\STATE $N \leftarrow N - 1$
\ENDIF
\ENDWHILE
\end{algorithmic}
\end{algorithm}

@@

In practice, we may
want to ask a question that is different from the central issue.
For example, suppose we want to know the value of $x$ to within a tolerance
of $\pm 1$. Any of the following statements would resolve the issue:
\begin{itemize}
\item $x \in \{1, 2, 3\}$, $x \notin \{1, 2, 3\}$,
                or anything that implies one of these
\item $x \in \{2, 3, 4\}$, $x \notin \{2, 3, 4\}$,
                or anything that implies one of these ...
\item ... $x \in \{999999998, 999999999, 1000000000\}$,
            $x \notin \{999999998, 999999999, 1000000000\}$,
                or anything that implies one of these
\end{itemize}

>>>>

\usepackage{dsfont}
\usepackage[utf8]{inputenc}
\usepackage{algorithm, mathtools}
\usepackage[noend]{algpseudocode}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{natbib}
\usepackage{enumerate}
\usepackage{microtype}

@@

This is difficult to compute because the expression
for the posterior distribution
\begin{align}
p(\x | \d) &= \frac{p(\x)p(\d | \x)}{p(\d)}
\end{align}
contains the marginal likelihood or `evidence'
\begin{align}
p(\d) &= \int p(\x) p(\d | \x) \, d\x.
\end{align}

@@

\begin{algorithm}
\begin{algorithmic}
\State {\em Set the numerical parameters:}
\State $N \in \{1, 2, 3, ... \}$
            \Comment{the number of Nested Sampling particles to use}
\State $\epsilon \geq 0$
            \Comment{the tolerance} \\
\hrulefill
\State $\widehat{\mathbf{h}} \leftarrow [\,]$
            \Comment{Initialise an empty list of results}

\While{more iterations desired}
    \State Generate $\x_{\rm ref}$ from $p(\x)$
            \Comment{Generate a reference point}
    \State $k \leftarrow 0$
            \Comment{Initialise counter}
  {\color{green}
    \State Generate $\left\{\x_i\right\}_{i=1}^N$ from $p(\x)$
            \Comment{Generate initial NS particles}
    \State Calculate $d_i \leftarrow d(\x_i; \x_{\rm ref})$ for all $i$
            \Comment{Calculate distance of each particle from the reference
                     point}
    \State $i^* \leftarrow \textnormal{argmin}(\lambda i \rightarrow d_i)$
            \Comment{Find the worst particle (greatest distance)}
%%    \While{$d_{\rm max} > \epsilon$}
%%        \State Blah
%%    \EndWhile

  } % \color{green}
\State More to come...
\EndWhile
\end{algorithmic}
\caption{Calculates $H_{\x} = -\int p(\x) \log p(\x) \, d\x$
         without evaluating $\log p(\x)$.}
\end{algorithm}

@@

In practice, we may
want to ask a question that is different from the central issue.
For example, suppose we want to know the value of $x$ to within a tolerance
of $\pm 1$. Any of the following statements would resolve the issue:
\begin{itemize}
\item $x \in \{1, 2, 3\}$ and anything that implies it
\item $x \in \{2, 3, 4\}$ and anything that implies it
\item $x \in \{3, 4, 5\}$ and anything that implies it
\item and so on.
\end{itemize}
